\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-10 fully-abstract-comp/popl2019/paper.tex
Introduction to Section 5.

\section{Proving full abstraction}
\label{sec:fa-proof}
\todo[inline]{Write small introduction. Maybe something about the difficulty of full-abstraction proofs (with references?) but mention that this is easier than some other cases (reference approximate back translation?) because back translation is trivial.}
% \begin{itemize}
% \item Logical relation
% \item FTLR
% \item Sketch high-level structure of the proof
% \end{itemize}

\subsection{Logical relation}
\label{subsec:logical-relation}
The backbone of the full-abstraction proof is a cross language, step-indexed, Kripke logical relation.
\todo[inline]{write a bit more introduction that informally tells the purpose of this logical relation in relation to the full proof.}
Unfortunately due to space considerations, we do not give a comprehensive description of it.
Instead we highlight the parts specific to the logical relation we have used and refer to the technical report~\citep{technical_report} for the details and to~\citet{skorstengaard_reasoning_2017} for a more comprehensive description of a logical relation for a capability machine.
Finally for the sake of presentation, we will sometimes omit describing details, such as step indexing, that are important for the correctness but otherwise not interesting.

>>>>

\section{Proving full abstraction}
\label{sec:fa-proof}
%\todo[inline]{Write small introduction. Maybe something about the difficulty of full-abstraction proofs (with references?) but mention that this is easier than some other cases (reference approximate back translation?) because back translation is trivial.}
% \begin{itemize}
% \item Logical relation
% \item FTLR
% \item Sketch high-level structure of the proof
% \end{itemize}
The backbone of the full-abstraction proof is a cross language, step-indexed, Kripke logical relation.
It relates the observable behavior of \srccm{} to the observable behavior of \trgcm{}.
In the full-abstraction proof, it allows us to transfer termination assumptions between the two machines which enables the use of a contextual equivalence assumption.
We first give an informal presentation of the logical relation before we return to a sketch of the full-abstraction proof.

\subsection{Logical relation}
\label{subsec:logical-relation}
In this section, we present the logical relation.
Unfortunately due to space considerations, we do not give a comprehensive description of it.
Instead we highlight the parts specific to the logical relation we have used and refer to the technical report~\citep{technical_report} for the details and to~\citet{skorstengaard_reasoning_2017} for a more comprehensive description of a logical relation for a capability machine.
Finally for the sake of presentation, we will sometimes omit describing details, such as step indexing, that are important for the correctness but otherwise not interesting.
